\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-23 icse20/eval.tex
Renamed directory icse -> icse20

\begin{table}[t]
  \caption{Number of productions in specifications,
from \textit{all} of which \( \tool \) automatically generated parsers}
  \label{fig:syntax-all-version}
  \[
    \begin{array}{c?r|r|r|r|r?r}
      \textbf{Version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \multicolumn{1}{c}{\textbf{avg.}}\\\toprule
      \text{\# Lexical prod.}
      & \text{78}
      & \text{78}
      & \text{78}
      & \text{81}
      & \text{81}
      & \text{79.2}\\\hline
      \text{\# Syntactic prod.}
      & \text{157}
      & \text{167}
      & \text{167}
      & \text{174}
      & \text{175}
      & \text{168}\\
    \end{array}
  \]
  \[
    \begin{array}{c|r|r|r|r?r}
      \textbf{Old version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c?}{\textbf{2019}}
      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
      \textbf{New version}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \\\toprule
      \Delta \; \text{\# Lexical prod.}
      & \text{3}
      & \text{5}
      & \text{6}
      & \text{0}
      & \text{4.7}\\\hline
      \Delta \; \text{\# Syntactic prod.}
      & \text{140}
      & \text{15}
      & \text{8}
      & \text{2}
      & \text{55}\\
    \end{array}
  \]
\end{table}

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.46\textwidth}
    \includegraphics[width=\textwidth]{img/sem-all.png}
    \caption{Results for existing versions}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-delta.png}
    \caption{Results for differences between adjacent versions}
    \label{fig:semantics-all-version-delta}
  \end{subfigure}
  \caption{Number of steps for abstract algorithms in specifications, from which
\( \tool \) generated the JavaScript semantics}
  \label{fig:all-version}
\end{figure}

@@

For syntax, we measured the number of grammar productions for which
\textsf{Parser Generator} automatically generated parsers.  As summarized in
Figure~\ref{fig:syntax-all-version}, the average numbers of lexical and
syntactic grammar productions are 79.2 and 168, respectively.
In addition, the average numbers of annually updated lexical and
syntactic grammar productions between adjacent versions are 4.7
and 55, respectively.  We report that \( \tool \)
automatically generated parsers for \textit{all} the productions.

For semantics, we measured the number of steps in abstract algorithms that
\textsf{Algorithm Compiler} with the compile rules described in
Section~\ref{sec:impl} automatically covered.
Figure~\ref{fig:all-version} shows that \( \tool \) could
automatically extract semantics with the 91.60\% success rate on
average for existing specifications, and 90.43\% for changed or
newly defined steps.  Moreover, we found that algorithm steps in
built-in libraries are less covered than other language semantics
with 86.98\% success rates (86.09\% for updates).
It is due to the diverse writing styles to represent
their own specific functionalities.
However, steps in core language semantics are covered
with higher success rates 95.35\% (95.25\% for updates).

According to this evaluation, we believe that \( \tool \) effectively
reduces the efforts to extract the syntax and semantics of JavaScript
not only for developing them from scratch, but also for updating
existing ones.

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,803\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,217}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,064\\\hdashline
    Module tests& 642 \\\hdashline
    Inessential built-in object tests & \inred{XXXX}\\\hdashline
    Non-standard negative tests & 2,628\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XXXX} \\\hdashline
    Failed tests & \inred{XXXX} \\\bottomrule
  \end{tabular}
\end{table}

@@

\subsection{Adaptability}
We show the adaptability of \( \tool \) with one case study: applying
it to an incomplete feature proposal.  Because ECMAScript is an open
standard language, various proposals are available with their own
specification changes and tests by following the TC39 process.  A
separate repository~\cite{proposals} maintains such proposals with six
different stages: Stage 0 to Stage 3, Finished, and Inactive.  Each
proposal starts with Stage 0, and the TC39 committee regularly
examines Stage 3 proposals to decide their next stages.  If a proposal
is confirmed, the committee changes its stage to Finished and
integrates it into the next version of the ECMAScript specification.
Otherwise, the committee changes its stage to Inactive.  Thus, we
applied \( \tool \) to one Stage 3 proposal.
%https://github.com/tc39/proposal-optional-chaining

>>>>

\begin{table}[t]
  \caption{Number of productions in specifications,
from \textit{all} of which \( \tool \) automatically generated parsers}
  \label{fig:syntax-all-version}
\vspace*{-1em}
\small
  \[
    \begin{array}{c?r|r|r|r|r?r}
      \textbf{Version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \multicolumn{1}{c}{\textbf{avg.}}\\\toprule
      \text{\# Lexical prod.}
      & \text{78}
      & \text{78}
      & \text{78}
      & \text{81}
      & \text{81}
      & \text{79.2}\\\hline
      \text{\# Syntactic prod.}
      & \text{157}
      & \text{167}
      & \text{167}
      & \text{174}
      & \text{175}
      & \text{168}\\
    \end{array}
  \]
  \[
    \begin{array}{c|r|r|r|r?r}
      \textbf{Old version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c?}{\textbf{2019}}
      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
      \textbf{New version}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \\\toprule
      \Delta \; \text{\# Lexical prod.}
      & \text{3}
      & \text{5}
      & \text{6}
      & \text{0}
      & \text{4.7}\\\hline
      \Delta \; \text{\# Syntactic prod.}
      & \text{140}
      & \text{15}
      & \text{8}
      & \text{2}
      & \text{55}\\
    \end{array}
  \]
\end{table}

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.46\textwidth}
    \includegraphics[width=\textwidth]{img/sem-all.png}
    \caption{Results for existing versions}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/sem-delta.png}
    \caption{Results for differences between adjacent versions}
    \label{fig:semantics-all-version-delta}
  \end{subfigure}
  \caption{Number of abstract algorithm steps in specifications, from which
\( \tool \) generated the JavaScript semantics}
  \label{fig:all-version}
\vspace*{-1em}
\end{figure}

@@

%For syntax, we measured the number of grammar productions for which
%\textsf{Parser Generator} automatically generated parsers.  
%Table~\ref{fig:syntax-all-version} shows the number of grammar productions

For syntax, \( \tool \) automatically generated parsers for
\textit{all} the productions.  As Table~\ref{fig:syntax-all-version} shows,
the average numbers of lexical and syntactic productions are 79.2 and 168, respectively.
Also, the average numbers of annually updated lexical and
syntactic productions between adjacent versions are 4.7 and 55, respectively.

For semantics, Figure~\ref{fig:all-version} shows that \( \tool \)
automatically extracted semantics with the 91.60\% success rate on
average for existing specifications, and 90.43\% for updates.
We found that algorithm steps in
built-in libraries have lower success rates (86.98\% for specifications
and 86.09\% for updates) than core language semantics (95.35\%  for specifications
and 95.25\% for updates) because of diverse writing styles in
describing their own specific functionalities.

This results show that \( \tool \) effectively reduces the efforts to
extract the syntax and semantics of JavaScript not only for developing
them from scratch, but also for updating existing ones.

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
\vspace*{-.5em}
\small
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,803\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,217}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,064\\\hdashline
    Module tests& 642 \\\hdashline
    Inessential built-in object tests & \inred{XXXX}\\\hdashline
    Non-standard negative tests & 2,628\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XXXX} \\\hdashline
    Failed tests & \inred{XXXX} \\\bottomrule
  \end{tabular}
\vspace*{-1em}
\end{table}

@@

\subsection{Adaptability}
We show the adaptability of \( \tool \) with one case study: applying
it to an incomplete feature proposal.  Because ECMAScript is an open
standard language, various proposals are available with their own
specification changes and tests.  A
separate repository~\cite{proposals} maintains such proposals with six
different stages: Stage 0 to Stage 3, Finished, and Inactive.  Each
proposal starts with Stage 0, and the TC39 committee regularly
examines Stage 3 proposals to decide their next stages.  If a proposal
is confirmed, the committee changes its stage to Finished and
integrates it into the next version of the ECMAScript specification.
Otherwise, the committee changes its stage to Inactive.  Thus, we
applied \( \tool \) to one Stage 3 proposal.
%https://github.com/tc39/proposal-optional-chaining

### 2019-08-23 icse20/impl.tex
Renamed directory icse -> icse20

\section{Implementation}\label{sec:impl}
In this section, we describe the implementation detail of \( \tool \),
which is an open-source project\footnote{The URL of the tool is anonymized
due to a double-blind review process.}.

Our goal is to extract the JavaScript syntax and semantics from the
ECMAScript 2020 specification.  It is the next ECMAScript version
that is actively updated in its GitHub repository~\cite{es2020}
to be released in the next year.  Moreover, Ecma Technical Committee 39 (TC39)
officially provides the conformance test suite, Test262, for ECMAScript 2020.

\subsection{Excluded Language Features}\label{sec:exclusion}
We decided not to support the following language features in ECMAScript 2020:

\paragraph{Non-Strict Mode}
Since ECMAScript 5, JavaScript introduced strict mode to
\textit{intentionally} provide slightly different semantics.  It
provides more stable semantics by preventing unsafe actions or
throwing originally ignored errors.  However, the ECMAScript
specification states that ``Strict mode does not restrict or modify
any aspect of the ECMAScript semantics that must operate consistently
across multiple source text units.''  Thus, we decided to support only
strict mode of JavaScript to focus on the main contribution of this
paper.

@@

\subsection{Compile Rules for ECMAScript}
\begin{table}[t]
  \centering
  \caption{Compile rules in ECMAScript 2020}
  \label{table:rules}
\vspace*{-1em}
  \[
    \begin{array}{c?r|r|r|r|r|r|r}
      \text{Name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c|}{\code{Ref}}
      & \multicolumn{1}{c}{\code{SecNo}}\\\hline
      \text{\# Rules}
      & 17
      & 16
      & 8
      & 11
      & 33
      & 7
      & 21
    \end{array}
  \]
\end{table}

As we discussed in Section~\ref{sec:compiler}, \textsf{Algorithm Compiler}
requires compile rules to compile given abstract algorithms to \( \ires \)
functions.  In order to cover the entire ECMAScript 2020 specification,
we defined compile rules for only seven kinds as summarized in
Table~\ref{table:rules}.  The compile rule for statements, \( \code{Stmt} \),
contains \inred{XX} compile rules and generates \( \ires \) instructions.
The \( \code{Expr} \), \( \code{Cond} \), and \( \code{Value} \) compile
rules denote expressions, conditions, and values, respectively.  While
all of them generate \( \ires \) expressions, they represent different
contexts in the ECMAScript specification.  For example,
\( \code{Expr} \) represents a context where any expression can appear,
\( \code{Cond} \) denotes a context where any boolean-valued expression
can appear, and \( \code{Value} \) represents a context where a fully
evaluated value can appear.  The \( \code{Ty} \) compile rule denotes
type names and generates string primitives in \( \ires \).  The \( \code{Ref} \)
represents references such as identifier lookup and member accesses of
map-like structures.  It generates \( \ires \) reference expressions.
Finally, the \( \code{SecNo} \) compile rule denotes section numbers
like \( \code{9.5.12} \), and it converts such numbers to
corresponding name strings like \( \code{"ProxyExoticObject.Call"} \):
\begin{lstlisting}[style=myScalastyle]
lazy val SecNo =
  "9.5.12" ^^ { case x => "ProxyExoticObject.Call" } |||
  ...
\end{lstlisting}

@@

Each ECMAScript data type has several fields to store their relevant values.
We should implement such structures in order to correctly evaluate JavaScript
programs, but fields of ECMAScript data types could be abstract algorithms.
We call them \textit{method-like abstract algorithms} because they
implicitly get their receiver objects as arguments at callsites.
To mimic such implicit behaviors, we added a special variable
\( \code{this} \) as the first parameter of a method-like abstract algorithm,
and passed a receiver object at its callsite by modifying
\textsf{Algorithm Compiler}.  For example, an Environment Record has
the \textsf{DeleteBinding (N)} abstract algorithm as one of its fields.
Then, it gets two parameters, the special parameter \( \code{this} \)
and normal one \( \code{N} \).  Thus, the following algorithm step:
\begin{center}
  \includegraphics[width=0.22\textwidth]{img/method-like-example.png}
\end{center}
is compiled into the following \( \ires \) instruction:
\begin{lstlisting}[style=ires]
return DclRec.DeleteBinding(DclRec, N)
\end{lstlisting}

\vspace*{-.5em}
\paragraph{Built-in Objects}
In ECMAScript, built-in objects are pre-defined functions with several
built-in functions.  For example, \( \code{Array} \)
is the constructor of array objects, and its prototype
\( \code{Array.prototype} \) has built-in functions for array objects.
For instance, \( \code{[1,2,3].flat()} \) calls the
\( \code{Array.prototype.flat} \) built-in function with the array
\( \code{[1,2,3]} \).  Because built-in functions are also abstract
algorithms, each of them is automatically converted to an \( \ires \)
function.  However, the structures of built-in objects should be
manually implemented.  Thus, we implemented built-in objects in Scala
and connected their properties with the extracted \( \ires \) functions.

Some built-in objects that are explicitly referenced in abstract
algorithms are intrinsic objects.  Intrinsic objects have their own
aliased names summarized in Table 7 of Section 6.1.7.4
\textsf{Well-Known Intrinsic Objects}.  We extracted the alias
information into \textsf{Global Setting} to utilize it during evaluation.

>>>>

\section{Implementation}\label{sec:impl}
This section describes the implementation detail of our open-source
tool, \( \tool \)\footnote{The URL of the tool is anonymized due to a
double-blind review process.}.  We target
%aim to extract the syntax and semantics from 
ECMAScript 2020, which is actively updated in its
GitHub repository~\cite{es2020} to be released in the next year.

\subsection{Excluded Language Features}\label{sec:exclusion}
We decided not to support the following ECMAScript 2020 features:

\paragraph{Non-Strict Mode}
Since ECMAScript 5, JavaScript introduced strict mode to
\textit{intentionally} provide slightly different semantics.  It
provides more stable semantics by preventing unsafe actions or
throwing originally ignored errors.  However, the ECMAScript
specification states that ``Strict mode does not restrict or modify
any aspect of the ECMAScript semantics that must operate consistently
across multiple source text units.''  Thus, we decided to support only
strict mode to focus on the main contribution of this paper.

@@

\subsection{Compile Rules for ECMAScript}
\begin{table}[t]
  \centering
  \caption{Compile rules in ECMAScript 2020}
  \label{table:rules}
\vspace*{-1em}
  \[
    \begin{array}{c?r|r|r|r|r|r|r}
      \text{Name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c|}{\code{Ref}}
      & \multicolumn{1}{c}{\code{SecNo}}\\\hline
      \text{\# Rules}
      & 17
      & 16
      & 8
      & 11
      & 33
      & 7
      & 21
    \end{array}
  \]
\vspace*{-2em}
\end{table}

As we discussed in Section~\ref{sec:compiler}, \textsf{Algorithm Compiler}
requires compile rules to compile given abstract algorithms to \( \ires \)
functions.  In order to cover the entire ECMAScript 2020 specification,
we defined compile rules for only seven kinds as summarized in
Table~\ref{table:rules}.  The compile rule for statements, \( \code{Stmt} \),
contains 17 compile rules and generates \( \ires \) instructions.
The \( \code{Expr} \), \( \code{Cond} \), and \( \code{Value} \) compile
rules denote expressions, conditions, and values, respectively.  While
all of them generate \( \ires \) expressions, they represent different
contexts in the ECMAScript specification.  For example,
\( \code{Expr} \) represents a context where any expression can appear,
\( \code{Cond} \) denotes a context where any boolean-valued expression
can appear, and \( \code{Value} \) represents a context where a fully
evaluated value can appear.  The \( \code{Ty} \) compile rule denotes
type names and generates string primitives in \( \ires \).  The \( \code{Ref} \)
represents references such as identifier lookup and member accesses of
map-like structures.  It generates \( \ires \) reference expressions.
Finally, the \( \code{SecNo} \) compile rule denotes section numbers
like \( \code{9.5.12} \), and it converts such numbers to
corresponding name strings like \( \code{"ProxyExoticObject.Call"} \).
% \begin{lstlisting}[style=myScalastyle]
% lazy val SecNo =
%   "9.5.12" ^^ { case x => "ProxyExoticObject.Call" } |||
%   ...
% \end{lstlisting}

@@

Each ECMAScript data type has several fields to store their relevant values.
We should implement such structures in order to correctly evaluate JavaScript
programs, but fields of ECMAScript data types could be abstract algorithms.
We call them \textit{method-like abstract algorithms} because they
implicitly get their receiver objects as arguments at callsites.
To mimic such implicit behaviors, we added a special variable
\( \code{this} \) as the first parameter of a method-like abstract algorithm,
and passed a receiver object at its callsite by modifying
\textsf{Algorithm Compiler}.  For example, an Environment Record has
the \textsf{DeleteBinding (N)} abstract algorithm as one of its fields.
Then, it gets two parameters, the special parameter \( \code{this} \)
and normal one \( \code{N} \).  Thus, the following algorithm step:
\begin{center}
  \includegraphics[width=0.2\textwidth]{img/method-like-example.png}
\end{center}
is compiled into the following \( \ires \) instruction:
\begin{lstlisting}[style=ires]
return DclRec.DeleteBinding(DclRec, N)
\end{lstlisting}

\vspace*{-1em}
\paragraph{Built-in Objects}
In ECMAScript, built-in objects are pre-defined functions with several
built-in functions.  For example, \( \code{Array} \)
is the constructor of array objects, and its prototype
\( \code{Array.prototype} \) has built-in functions for array objects.
For instance, \( \code{[1,2,3].flat()} \) calls the
\( \code{Array.prototype.flat} \) built-in function with the array
\( \code{[1,2,3]} \).  Because built-in functions are also abstract
algorithms, each of them is automatically converted to an \( \ires \)
function.  However, the structures of built-in objects should be
manually implemented.  Thus, we implemented built-in objects in Scala
and connected their properties with the extracted \( \ires \) functions.
%
Some built-in objects that are explicitly referenced in abstract
algorithms are intrinsic objects, which have their own
aliased names summarized in Table 7 of Section 6.1.7.4
\textsf{Well-Known Intrinsic Objects}.  We extracted the alias
into \textsf{Global Setting} to utilize it during evaluation.

### 2019-08-23 icse20/parser.tex
Renamed directory icse -> icse20

\textbf{Solution: Lookahead Tokens.}
To alleviate the problem, we propose \textit{lookahead parsers},
which are recursive descent parsers extended with backtracking and
\textit{lookahead tokens}.  They keep track of the next possible
tokens by statically calculating first tokens of each symbol using the
algorithm in Figure~\ref{fig:first-tokens}.  For example, the
following steps explain how to utilize lookahead tokens during parsing
with the input \( \code{a(b);} \):
\begin{center}
  \includegraphics[width=0.3\textwidth]{img/laparser.png}
\end{center}
Each node \( \symb^*[\la] \) denotes a sequence of symbols \( \symb^* \)
with a set of lookahead tokens \( \la \).  The parsing process follows
a pre-order traversal.  It starts from the starting non-terminal \( \NT{A} \)
with the special lookahead \( \emptyfirst \), which denotes the end of
inputs.  Then, it visits the first alternative \( \NT{T} \T{;} \) with
the same lookahead.  Each symbol is visited with its corresponding
lookahead, which is the first tokens of the right next symbol.
For example, for the symbol \( \NT{T} \), the next symbol is \( \T{;} \)
and its first token is itself.  Thus, the parser visits \( \NT{T} \)
with the lookahead \( \T{;} \).  The most important point here
is the first alternative \( \T{a} \) of the
non-terminal \( \NT{T} \).  The parser visits it with the lookahead \( \T{;} \)
but the next token of the input string \( \code{a(b);} \) is \( \code{(} \)
rather than \( \code{;} \).  Hence, it fails to parse the input string
even though the current token is the same with the terminal \( \T{a} \).
Therefore, the parser can visit the next alternative \( \T{a}\T{(}\T{b}\T{)} \)
and successfully parsers the input \( \code{a(b);} \).

@@

\textbf{AST Generation.}
We first automatically generate ASTs as Scala case classes from a
given \( \bnfes \) grammar.  Because lexical grammars do not affect
the ECMAScript semantics, we represent them as string values.
For parser grammars, we automatically synthesize a Scala file that has
classes of syntax trees.  For each production \(
  \NT{A}(\param_1, \cdots, \param_k) ::=
  (\cond_1 \Rightarrow)^? \rhs_1 \mid
  \cdots \mid
  (\cond_n \Rightarrow)^? \rhs_n
\), the AST generator defines the \( \code{A} \) trait and multiple
subclasses \( \code{A}_i \) of \( \code{A} \) for \(1 \le i \le n\)
that represents its alternatives.  Each class \( \code{A}_i \) has
non-terminals in its corresponding alternative as its fields.
For instance, the \( ArrayLiteral \) production in Figure~\ref{fig:array-literal}
gets automatically translated to the following Scala classes:
\begin{lstlisting}[style=smallScalastyle]
trait ArrayLiteral extends AST
case class ArrayLiteral0(x1: Option[Elision])
case class ArrayLiteral1(x1: ElementList)
case class ArrayLiteral2(x1: ElementList, x3: Option[Elision])
\end{lstlisting}

>>>>

\textbf{Solution: Lookahead Tokens.}
To alleviate the problem, we propose \textit{lookahead parsers},
which are recursive descent parsers extended with backtracking and
\textit{lookahead tokens}.  They keep track of the next possible
tokens by statically calculating first tokens of each symbol using the
algorithm in Figure~\ref{fig:first-tokens}.  For example, the
following steps explain how to utilize lookahead tokens during parsing
with the input \( \code{a(b);} \):
\begin{center}
  \includegraphics[width=0.3\textwidth]{img/laparser.png}
\end{center}
Each node \( \symb^*[\la] \) denotes a sequence of symbols \( \symb^* \)
with a set of lookahead tokens \( \la \).  The parsing process follows
a pre-order traversal.  It starts from the starting non-terminal \( \NT{A} \)
with the special lookahead \( \emptyfirst \), which denotes the end of
inputs.  Then, it visits the first alternative \( \NT{T} \T{;} \) with
the same lookahead.  Each symbol is visited with its corresponding
lookahead, which is the first tokens of the right next symbol.
For example, for the symbol \( \NT{T} \), the next symbol is \( \T{;} \)
and its first token is itself.  Thus, the parser visits \( \NT{T} \)
with the lookahead \( \T{;} \).  The most important point here
is the first alternative \( \T{a} \) of the
non-terminal \( \NT{T} \).  The parser visits it with the lookahead \( \T{;} \)
but the next token of the input string \( \code{a(b);} \) is \( \code{(} \)
rather than \( \code{;} \).  Hence, it fails to parse the input string
even though the current token is the same with the terminal \( \T{a} \).
Therefore, the parser can visit the next alternative \( \T{a}\T{(}\T{b}\T{)} \)
and successfully parses the input \( \code{a(b);} \).

@@

\textbf{AST Generation.}
We first automatically generate ASTs as Scala case classes from a
given \( \bnfes \) grammar.  Because lexical grammars do not affect
the ECMAScript semantics, we represent them as string values.
For parser grammars, we automatically synthesize a Scala file that has
classes of syntax trees.  For each production \(
  \NT{A}(\param_1, \cdots, \param_k) ::=
  (\cond_1 \Rightarrow)^? \rhs_1 \mid
  \cdots \mid
  (\cond_n \Rightarrow)^? \rhs_n
\), the AST generator defines the \( \code{A} \) trait and multiple
subclasses \( \code{A}_i \) of \( \code{A} \) for \(0 \le i \le n-1\)
that represents its alternatives.  Each class \( \code{A}_i \) has
non-terminals in its corresponding alternative as its fields.
For instance, the \( ArrayLiteral \) production in Figure~\ref{fig:array-literal}
gets automatically translated to the following Scala classes:
\begin{lstlisting}[style=smallScalastyle]
trait ArrayLiteral extends AST
case class ArrayLiteral0(x1: Option[Elision])
case class ArrayLiteral1(x1: ElementList)
case class ArrayLiteral2(x1: ElementList, x3: Option[Elision])
\end{lstlisting}

### 2019-08-23 icse20/related.tex
Renamed directory icse -> icse20

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in the ECMAScript specification.  KJS~\citet{kjs} and
JaVerT\citet{javert} defined formal semantics of JavaScript by manually converting
the ECMAScript specification to their own formal languages.  KJS mapped
ECMAScript 5 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a framework to generate converters from the
specification to IR with a conversion assistant and layered translation
techniques, which reduces human efforts significantly.

>>>>

Several approaches have defined the formal semantics of JavaScript.
\citet{lambdajs} defined a core calculus of JavaScript, and expressed the
rest as desugaring.  While it presents the core JavaScript semantics in
an extension of the $\lambda$ calculus, it does not show the semantics
correspondence defined in the ECMAScript specification.  KJS~\citet{kjs} and
JaVerT~\citet{javert} defined formal semantics of JavaScript by manually converting
the ECMAScript specification to their own formal languages.  KJS mapped
ECMAScript 5.1 in the K framework~\cite{kframework}, which can be used
for program verification and analysis.  Similarly, JaVerT converts the
specification to their own IR called JSIL to make further analysis.
Our approach provides a framework to generate syntactic parsers and
semantics compilers from the specification to \( \ires \)
with a conversion assistant, which reduces human efforts significantly.
